Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-05 manuscript/climate_sensitivity_draft.Rmd
fixed AIC significance error (not sure how this came in)

Models were run for all drought years combined and for each drought year individually. In order to determine the relative importance of each predictor variable individually, we first implemented models with the variable in question as a fixed effect, along with drought year (for model with all drought years combined) and $ln[H]$ (included in null models because of it's substantial influence). **Variables were considered to have significant influence on $Rt$ when AICc was reduced by $\ge$ 1 unit relative to the corresponding null model lacking that variable (Table 4). **

>>>>

Models were run for all drought years combined and for each drought year individually. In order to determine the relative importance of each predictor variable individually, we first implemented models with the variable in question as a fixed effect, along with drought year (for model with all drought years combined) and $ln[H]$ (included in null models because of it's substantial influence). Variables were considered to have significant influence on $Rt$ when AICc was reduced by $\ge$ 2.0 relative to the corresponding null model lacking that variable (Table 4).
